---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# golemize

Example of turning a classical standard app to `{golem}`.

## From github.com/rstudio/shiny-examples/060-retirement-simulation

### Structure

Shiny Example : 

```{r}
fs::dir_tree("060-retirement-simulation")
```

`{golem}` example: 

```{r}
fs::dir_tree("060-retirement-simulation-golem")
```


### Where to put things 

#### CSS & metadata

In `{golem}`, the external dependencies goes into `inst/app/www`. Then, they need to be linked to in `app_ui.R`, in `golem_add_external_resources()`. If you're creating the file with `add_css_file()` for example, the file will be opened and you'll have in your console the piece of code to copy into app_ui.R.

+ For the example app, the css from [`www/simplex.min.css`](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/www/simplex.min.css) goes into [`inst/app/www/simplex.min.css`](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/inst/app/www/simplex.min.css). It's linked in `app_ui.R`, inside the [`golem_add_external_resources()`](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/R/app_ui.R#L56) function.

+ DESCRIPTION file > DESCRIPTION FILE 

#### Server

Take your server.R file, and split it into pieces. The body of the main server function foes into the function skeleton in `R/app_server.R`. The other server functions can be placed in other files in the R/folder. The data defined can either be defined as golem options or it can be created as a package data.

+ The [functions from the server](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/server.r#L5) can be put in `R/`, as classical package functions, for example [`utils_server.R`](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/R/utils_server.R)

+ The [server function](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/server.r#L108) goes into [app_server.R](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/R/app_server.R)

+ [data](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/server.r#L1) can be created as [package data](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/data-raw/DATASET.R).

#### UI

Same dance for the UI part.

+ The [functions from the UI](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/ui.r#L3) can be put in `R/`, as classical package functions, for example [`utils_ui.R`](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/R/utils_ui.R)

+ The [UI](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/ui.r#L26) function goes to [app_ui.R](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/R/app_ui.R#L7)

#### Dep

+ Instead of [library(shiny)](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation/ui.r#L1), we list `{shiny}` as a [dependency](https://github.com/ColinFay/golemize/blob/master/060-retirement-simulation-golem/DESCRIPTION#L11).

## Launch the `{golem}`

+ You can run the whole `dev/run_dev.R` script. 

+ You can run `pkgload::load_all();mygolem::run_app()`